Social Participation Ontology: community documentation, enhancements and use examples

### 2015-09-20 paper.tex
social participation nas keywords do pdf do arxiv

\pacs{89.65-s,07.05.Bx,07.05.Kf}% PACS, the Physics and Astronomy
\keywords{OWL, semantic web, linked data, electronic democracy, participatory democracy, social systems}%Use showkeys class option if keyword
\maketitle

>>>>

\pacs{89.65-s,07.05.Bx,07.05.Kf}% PACS, the Physics and Astronomy
\keywords{OWL, semantic web, linked data, electronic democracy, participatory democracy, social participation, social systems}%Use showkeys class option if keyword
\maketitle
